Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-07 draft.tex
changes

The key insight is that there exists a filtration on our model for the $E_n$-center $\bZ_n(\fg)$ and the $E_n$-enveloping algebra $\bU_n (\fg)$ whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.

@@

There is another geometric model \brian{finish}
The idea is too look at configurations of disks and half-disks inside of the upper-half space $\HH^{n+1} = \{(x_1,\ldots, x_{n+1}) \; | \; x_{n+1} \geq 0\}$. 
What results is a two-colored operad known as the $(n+1)$-dimensional Swiss cheese operad where the two colors correspond to disks and half-disks.

There is another geometric picture for algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of constructible factorization algebras on $(n+1)$-manifolds with boundary.
One drawback of the previous section is that we did not provide a model for the $E_n$-center of an enveloping algebra as a constructible factorization algebra on an $(n+1)$-dimensional manifold with boundary.

A constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a pair of factorization algebras $(\pi_* \bA , \bA_{\partial})$ on $M$ which define a factorization pair as in Definition \ref{dfn:pair}.

The next goal of this section is to provide a model of the classical limit of the $\EE_n$-center as a constructible factorization algebra.

@@

\begin{prp}
Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
There is a constructible commutative factorization algebra ${\bf C}_n (\fg)$
%\begin{equation}\label{eqn:graded}
%\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
%\end{equation}
on $M \times \RR_{\geq 0}$ such that the pair 
\[
(\pi_* {\bf C}_n (\fg), {\bf C}_n (\fg)_\partial)
\]
is equivalent to the pair $({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg))$ as commutative factorization algebras \brian{adjectives}
\end{prp}

@@

\begin{lmm}
These filtrations equip the pair $(\bZ_n (\fg), \bU_n(\fg))$ with the structure of a filtered \brian{name}.
Moreover, the associated graded pair $({\rm Gr} \; \bZ_n (\fg), {\rm Gr} \; \bU_n(\fg))$ is a commutative \brian{name}. 
\end{lmm}
\begin{proof}
One has
\[
{\rm Gr} \; \UU_n (\fg) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c [1] \right)
\]
and
\[
{\rm Gr} \; \bZ_n (\fg) = \clie^\bu\bigg(\fg \otimes \Omega^\bu \; , \; {\rm Sym} \left(\fg \otimes \Omega^\bu_c [1]\right) \bigg) 
\]
as factorization algebras. 
These are both commutative by direct inspection. 
\end{proof}

@@

\subsection{The bulk factorization algebra}

@@

\begin{dfn}
For an open set $U \subset M \times \RR_{>0}$ let $\overset{\circ}{\bf Z}_n(\fg) (U)$ be the cochain complex 
\[
\overset{\circ}{\bf Z}_n(\fg) (U) = \clie \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
\]
The assignment $U \mapsto \overset{\circ}{\bf Z}_n(\fg) (U)$ defines a locally constant factorization algebra on $M \times \RR_{>0}$. 
\end{dfn}

@@

\begin{dfn}\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\overset{\circ}{\bf Z}_n (\fg)(U)$.
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(V)$. 
\end{itemize}
\brian{not sure how much to say about structure maps}
\end{dfn}

On each open set $U$, the cochain complex $\Tilde{\bZ}_n(\fg) (U)$ is actually a commutative dg algebra. 
In fact, it has the structure of a $\PP_0$-algebra where the $1$-shifted bracket $\{\cdot, \cdot\}$ is defined as follows.

>>>>

The key insight is that there exists a filtration on our model for the $\EE_n$-center $\bZ_n(\fg)$ and the $\EE_n$-enveloping algebra $\bU_n (\fg)$ whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.

@@

%The idea is too look at configurations of disks and half-disks inside of the upper-half space $\HH^{n+1} = \{(x_1,\ldots, x_{n+1}) \; | \; x_{n+1} \geq 0\}$. 
%What results is a two-colored operad known as the $(n+1)$-dimensional Swiss cheese operad where the two colors correspond to disks and half-disks.

In the previous section, we mentioned another geometric model for algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of constructible factorization algebras on $(n+1)$-manifolds with boundary.
One drawback of the previous section is that we did not provide a model of this type for the $\EE_n$-center of an enveloping algebra. 
The next goal of this section is to provide a model of the classical limit of the $\EE_n$-center as a constructible factorization algebra.

Any constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a factorization pair $(\pi_* \overset{\circ}{\bA} , \bA_{\partial})$ in the sense of Definition \ref{dfn:pair}.
We recall this construction in Section \ref{sec:bulk}. 
In particular, on the upper half space $\HH^n$, a constructible factorization algebra determines an algebra over the $(n+1)$-dimensional Swiss cheese operad.

@@

\begin{prp}\label{prp:pair}
Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
There is a constructible commutative factorization algebra ${\bf C}_n (\fg)$
%\begin{equation}\label{eqn:graded}
%\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
%\end{equation}
on $M \times \RR_{\geq 0}$ such that the pair 
\[
(\pi_* \overset{\circ}{\bf C}_n (\fg), {\bf C}_n (\fg)_\partial)
\]
is equivalent to the pair $({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg))$ as commutative factorization algebras \brian{adjectives}
\end{prp}

@@

\begin{lmm}
These filtrations equip $(\bZ_n (\fg), \bU_n(\fg))$ with the structure of a filtered factorization pair.
Moreover, the associated graded pair $({\rm Gr} \; \bZ_n (\fg), {\rm Gr} \; \bU_n(\fg))$ is a commutative factorization pair. 
\end{lmm}
\begin{proof}
One has
\[
{\rm Gr} \; \UU_n (\fg) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c [1] \right)
\]
and
\[
{\rm Gr} \; \bZ_n (\fg) = \clie^\bu\bigg(\fg \otimes \Omega^\bu \; , \; {\rm Sym} \left(\fg \otimes \Omega^\bu_c [1]\right) \bigg) 
\]
as factorization algebras. 
These are both commutative by direct inspection. 
\end{proof}

@@

\subsection{The bulk factorization algebra} \label{sec:bulk}

@@

\begin{dfn}
For an open set $U \subset M \times \RR_{>0}$ let $\overset{\circ}{\bC}_n(\fg) (U)$ be the cochain complex 
\[
\overset{\circ}{\bC}_n (\fg) (U) = \clie \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
\]
\end{dfn}

The assignment $U \mapsto \overset{\circ}{\bC}_n(\fg)(U)$ defines a locally constant factorization algebra on $M \times \RR_{>0}$. 
In fact, it extends to a constructible factorization algebra on $M \times \RR_{\geq 0}$ in the following way.

To state the definition, we will make use of the following map of cochain complexes.

\begin{dfn}\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\overset{\circ}{\bC}_n (\fg)(U)$.
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(V)$. 
\end{itemize}
The structure map associated to the embedding 
\[
U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\]
is
\[
\clie \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V) [1] \right) 
\]
\end{dfn}

On each open set $U \subset M \times \RR_{\geq 0}$, the cochain complex $\bC_n(\fg) (U)$ is a commutative dg algebra. 
In fact, it has the structure of a $\PP_0$-algebra where the $1$-shifted bracket $\{\cdot, \cdot\}$ is defined as follows.

Suppose $\bA$ is any constructible factorization algebra on a manifold with boundary $M \times \RR_{\geq 0}$. 
Then, restricting to the boundary $M$, we obtain a locally constant factorization algebra that we will denote by $\bA_{\partial}$. 
Likewise, we can restrict to the bulk $M \times \RR_{> 0}$ and pushforward along $\pi : M \times \RR_{> 0} \to M$ to obtain another locally constant factorization algebra on $M$ that we will denote by $\pi_* \overset{\circ}{\bA}$. 
It is immediate to check that $(\pi_* \overset{\circ}{\bA} , \bA_{\partial})$ form a factorization pair in the sense of Definition \ref{dfn:pair}.

@@
